Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Explain Node class in RapidGL

>>>>

Core to RapidGL is the {\tt Node} class.  Nodes can override the {\tt visit}
method to perform actions when the scene is traversed.  Most implementations
perform any setup which requires other nodes the first time they are visited.
For example, many nodes check for ancestors with specific types or search the
scene for nodes with a specific ID.  Nodes can also register themselves as {\em
listeners} of other nodes by implementing the {\tt NodeListener} interface and
passing a pointer to the node's {\tt addNodeListener} method.
